\documentclass[12pt]{article} % use larger type; default would be 10pt
\usepackage[margin=1in]{geometry} % to change the page dimensions
         % otherwise the current date is printed 
%\usepackage{times}
\usepackage{times}
\usepackage{fancyhdr}
\usepackage{xspace}


\pagestyle{fancy}
\lhead{Kristin Stephens}
\rhead{\thepage}
%\cfoot{}

\begin{document}
\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\parindent}{0pt} %Remove indent of all but first paragraph
\setlength{\parskip}{2ex} %Add space between paragraphs

Edit this and following text.

Cupcake ipsum dolor sit.
Amet icing candy tiramisu apple pie biscuit cheesecake wafer cotton candy. Donut gummi bears muffin gingerbread croissant lollipop faworki. Sweet roll pastry sugar plum pie wypas. Brownie lollipop chocolate ice cream halvah muffin pudding. Pudding wafer powder dragée jelly soufflé oat cake. Pastry gummies cookie toffee.
Cotton candy cake caramels marzipan applicake wafer lollipop tart dessert. Ice cream chocolate caramels dessert cake gummies sesame snaps gingerbread. Cupcake carrot cake gummies. Marzipan marshmallow topping liquorice applicake gingerbread pie pudding.

Chocolate cake gummies dessert icing applicake jujubes wypas jelly-o marshmallow. Fruitcake chocolate cake pastry sesame snaps croissant powder.
Jelly-o dessert cookie croissant. Cheesecake lollipop tiramisu powder. Marshmallow carrot cake pastry cotton candy cupcake gummi bears danish. Sugar plum toffee marzipan muffin croissant dragée halvah jujubes dessert.
Candy canes pie soufflé jelly beans soufflé. Sugar plum macaroon bear claw caramels applicake chocolate bar.
Toffee cheesecake candy dessert chocolate bar marshmallow muffin. Cake brownie pudding liquorice marshmallow icing. Oat cake topping jelly. Tiramisu donut croissant applicake pie cupcake. Toffee muffin jelly-o sweet roll faworki gummi bears lemon drops faworki caramels. Pie soufflé chocolate powder marzipan. Candy cookie faworki candy canes lemon drops cookie lemon drops.
Halvah sugar plum jujubes chocolate lollipop.

\end{document}
